{\bf {\Large Evaluation and correction of noise related to physical processes in estimates of estuary metabolism}}

### 2014-07-30 assess.Rnw
commit before going back to old wrtds approach using int grd for normalization

An example from Sapelo Island further highlights the effects of weighted regression on metabolism estimates (\cref{fig:case_ex1}).  Tidal predictions for Sapelo Island indicated that the site is strongly semidiurnal with approximately two tidal peaks per 24 hour period.  Tidal ffects on the observed \ac{DO} time series were apparent such that semidiurnal variation is closely correlated to tidal height variation.  Weighted regression was successful in removing the variation in the observed \ac{DO} time series from changes in tidal height.  The detided \ac{DO} time series exhibited more consistent diel variation with photoperiod (i.e., one peak per 24 hours) as compared to the observed time series (i.e., two peaks per 24 hours).  However, metabolism before and after detiding for the period of observation was similar, suggesting that detiding the \ac{DO} signal does not have a large effect on daily integerated metabolism estimates.

>>>>

An example from Sapelo Island further highlights the effects of weighted regression on metabolism estimates (\cref{fig:case_ex1}).  Tidal predictions for Sapelo Island indicated that the site is strongly semidiurnal with approximately two tidal peaks per 24 hour period.  Tidal ffects on the observed \ac{DO} time series were apparent such that semidiurnal variation is closely correlated to tidal height variation.  Weighted regression was successful in removing the variation in the observed \ac{DO} time series from changes in tidal height.  The detided \ac{DO} time series exhibited more consistent diel variation with photoperiod (i.e., one peak per 24 hours) as compared to the observed time series (i.e., two peaks per 24 hours).  However, metabolism before and after detiding for the period of observation was similar, suggesting that detiding the \ac{DO} signal does not have a large effect on mean daily integerated metabolism estimates.

### 2014-07-30 swmp_noise.Rnw
commit before going back to old wrtds approach using int grd for normalization

@@

# subset metab estimates by 30 day window and tide prop 1
load('case_grds.RData')
sel_vec <- with(case_grds, which(Day == 30 & Tide == 1))

@@

# aggregate by weekly, monthly, seasonal categories

>>>>

% example from SAPDC
\centering\vspace*{\fill}
<<case_ex1, cache = T, fig.height = 7.5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Example of metabolism and \\ac{DO} time series before (observed) and after (detided) weighted regression. Results are for a ten day period in March for the Sapelo Island station using a weighted regression with a window of thirty days and tidal height proportion of one.'>>=
######
# SAPDC example

load('met_ls_inst.RData')
load('met_ls.RData')
load('case_grds.RData')

# subsets by case. date range, window comb
case <- 'SAPDC'
dat.rng<-as.Date(c('2012-03-20','2012-03-29')) 
sel_vec <- with(case_grds, which(Day == 30 & Tide == 1))
sel_vec <- paste0(case, '_wtreg_', sel_vec, '.RData')

# select case, window
met_subs <- met_ls[[grep(sel_vec, names(met_ls))]]
inst_subs <- met_ls_inst[[grep(sel_vec, names(met_ls))]]

# subset yby date
met.rng <- met_subs$Date<=dat.rng[2] & met_subs$Date>=dat.rng[1]
met_subs <- met_subs[met.rng,]

inst_subs$Date <- as.Date(inst_subs$DateTimeStamp)
inst.rng <- inst_subs$Date<=dat.rng[2] & inst_subs$Date>=dat.rng[1]
inst_subs <- inst_subs[inst.rng,]

##
# custom theme, mod of theme_bw

my_theme <- theme(
  legend.title = element_blank(),legend.position = 'top',
  axis.title.x = element_blank(),legend.box= 'horizontal',
  plot.margin= unit(c(0, 1, 0, 1), "lines") # top right bottom left
  )

# function for setting range on y axis
rng.fun<-function(vec.in){
  rngs<-range(vec.in,na.rm=T)
  buffs<-0.07*abs(diff(rngs))
  c(rngs[1]-buffs,rngs[2]+buffs)
  }

##
# metab plot
to_plo1 <- melt(met_subs, id.var = c('Date'), 
  measure.var = grep('Pg|Rt|NEM', names(met_subs), value = T)
  )
to_plo1$Input <- 'Observed'
to_plo1$Input[grep('dtd', to_plo1$variable)] <- 'Detided'
to_plo1$Input <- factor(to_plo1$Input, levels = c('Observed', 'Detided'))
to_plo1$variable <- gsub('_dtd', '', to_plo1$variable)

ylab<-expression(paste('DO (g ',m^-2, d^-1, ')'))
p1 <- ggplot(to_plo1, aes(x = Date, y = 0.032 * value, group = variable,
    colour = variable)) +
  geom_line() +
  theme_bw() +
  geom_point(size = 2) +
  facet_wrap(~Input, ncol = 1) +
  scale_y_continuous(ylab)  +
  my_theme

##
# DO plot
to_plo2 <- met.day.fun(inst_subs, case)
names(to_plo2)[names(to_plo2) %in% 'variable'] <- 'solar'
ggpoly <- poly.fun(to_plo2$solar, to_plo2)

ylab<-expression(paste('DO (mg ',L^-1,')'))
p2 <- ggplot(to_plo2, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = DO_obs, colour = 'Observed')) +
  geom_line(aes(y = DO_dtd, colour = 'Detided')) +
  coord_cartesian(ylim = c(0,9)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +
  scale_y_continuous(ylab)  +
  my_theme

## 
# tide plot
to_plo3 <- met.day.fun(inst_subs, case)
names(to_plo2)[names(to_plo2) %in% 'variable'] <- 'solar'
ggpoly <- poly.fun(to_plo2$solar, to_plo2)

ylab<-expression(paste('Height (m)'))
p3 <- ggplot(to_plo3, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = Tide, colour = TotPAR)) +
  coord_cartesian(ylim = rng.fun(to_plo3$Tide)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +  
  my_theme + 
  scale_y_continuous(ylab) +
  scale_colour_gradient("PAR", low='blue', high='yellow',
    guide = guide_colorbar(direction = "horizontal",barheight= 0.3))

# Get the widths
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
pC <- ggplot_gtable(ggplot_build(p3))
maxWidth = unit.pmax(pA$widths[2:3], pB$widths[2:3], 
                     pC$widths[2:3])

# Set the widths
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth
pC$widths[2:3] <- maxWidth

grid.arrange(pA, pB, pC, ncol = 1, heights = c(1.7, 1, 1))

@@

# subset metab estimates by 30 day window and tide prop 1
load('case_grds.RData')
sel_vec <- with(case_grds, which(Day == 15 & Tide == 1))

@@

# aggregate by weekly, monthly, seasonal categories
# for each case...
agg_sum <- llply(met_sub, 
  .fun = function(x){

    # metabolism column names
    met_cols <- c('Pg', 'Rt', 'NEM', 'Pg_dtd', 'Rt_dtd', 'NEM_dtd')

    # melt by weekly, monthly, seasonal cats
    x <- melt(x, measure.var = c('week', 'month', 'seas'), 
      id.var = c('Date', met_cols)
      )

    agg_res <- dlply(x,
      .var = c('variable'), 
      .fun = function(y){

        out <- vector('list', length = length(met_cols))
        names(out) <- met_cols
        for(met in met_cols){

          tmp <- summarySE(y, measurevar = met, groupvars = 'value',
            narm = T) 
          names(tmp)[names(tmp) %in% met] <- 'mean'
          out[[met]] <- tmp

        # combine metabolism categories 
        out <- melt(out, id.var = names(out[[1]]))
        names(out)[names(out) %in% 'L1'] <- 'var'
        out

    # combine time categories
    agg_res <- melt(agg_res, id.var = names(agg_res[[1]]))
    names(agg_res)[names(agg_res) %in% 'L1'] <- 'cats'

    # separate var column into metabolis, obs/dtd
    agg_res$var[!grepl('dtd',agg_res$var)] <- paste0(
      agg_res$var[!grepl('dtd',agg_res$var)], '_obs')

    agg_res$sub_var <- gsub('^[A-Z,a-z]*_', '', agg_res$var)
    agg_res$var <- gsub('_[a-z]*$', '', agg_res$var)

    agg_res

to_plo <- agg_sum[[1]]

p <- ggplot(to_plo, aes(x = factor(value), y = mean, group = sub_var,
    colour = sub_var)) +
  geom_line() + 
  facet_wrap(cats ~ var, scales = 'free') +
  theme_bw()
@
\vfill
\clearpage

### 2014-07-30 swmp_noise.tex
commit before going back to old wrtds approach using int grd for normalization

>>>>

% example from SAPDC
\centering\vspace*{\fill}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[!ht]

{\centering \includegraphics[width=0.8\textwidth]{figure/case_ex1}

\caption[Example of metabolism and \ac{DO} time series before (observed) and after (detided) weighted regression]{Example of metabolism and \ac{DO} time series before (observed) and after (detided) weighted regression. Results are for a ten day period in March for the Sapelo Island station using a weighted regression with a window of thirty days and tidal height proportion of one.\label{fig:case_ex1}}
\end{figure}

% plots of summarized metabolism estimates, before/after detiding
\centering\vspace*{\fill}

\vfill
\clearpage
